Verifying synchronous distributed algorithms using IVy

### 2018-08-06 paper/paper.tex
- page 11, section (IV.ii): give more intuition about the encoding. Maybe 	explain in words the meaning of one function/relation of each 	graph/state/communication parts of the node

\subsection{Types, functions, relations}
First the types, functions, relations and individual variables that are used throughout the program are presented:

\begin{mdframed}[backgroundcolor=light-gray, roundcorner=10pt,leftmargin=1, rightmargin=1, innerleftmargin=15, innertopmargin=15,innerbottommargin=15, outerlinewidth=1, linecolor=light-gray]
\begin{lstlisting}
type node
type value
object node = {
  #graph/system related
  function val(X:node) : value
  function default(X: node) : value
  individual def : value
  relation failed(A:node)
  relation failed_before_round(A:node)
  relation failed_during_round(A:node)
  relation has_single_value(N:node)

  #state
  relation w(SELF:node, V:value)
  relation decision(SELF:node, VALUE:value)

  #communication
  relation message(N:node, V:value)
  relation incomming_message(SELF:node, OTHER:node)
  relation incomming_message_failing(SELF:node, OTHER:node)
}

object system = {
  individual decision_round:bool
  individual clean_round_occured:bool
}
\end{lstlisting}
\end{mdframed}

\noindent Their meaning will become clear as the code is presented in the following paragraphs.

>>>>

\subsection{Types, functions, relations}
First the types, functions, relations and individual variables that are used throughout the program are presented. They are annotated with comments explaining their purpose.  Their meaning will become more clear as the code is presented in the following paragraphs.

\begin{mdframed}[backgroundcolor=light-gray, roundcorner=10pt,leftmargin=1, rightmargin=1, innerleftmargin=15, innertopmargin=15,innerbottommargin=15, outerlinewidth=1, linecolor=light-gray]
\begin{lstlisting}
type node
type value
object node = {

#graph/system
  # stores the initial value of each X
  function val(X:node) : value

  # stores the default value of the network
  individual def : value

  # stores the default value that each node stores independently
  function default(X: node) : value

  # failed(a) is true if node a failed
  relation failed(A:node)

#state
  # w(n, v) denotes whether n's w contains value v
  relation w(SELF:node, V:value)

  # decision(n, v) denotes whether n has decided on v
  relation decision(SELF:node, VALUE:value)

#communication
  # message(n,v) denotes whether v is broadcast by n
  relation message(N:node, V:value)

  # incomming_message(n,o) denotes whether node n received a message
  # from node o
  relation incomming_message(SELF:node, OTHER:node)

# internal helpers
  # true if a node had already failed before this round
  relation failed_before_round(A:node)

  # true if a node failed during this round
  relation failed_during_round(A:node)

  # true if a node has a single value in w
  relation has_single_value(N:node)

  # helper to simulate non-determinstic message sending
  relation incomming_message_failing(SELF:node, OTHER:node)

}

object system = {
  # true if current round is decision round
  individual decision_round:bool

  # true if a clean round occured in the past, or the current round
  individual clean_round_occured:bool
}
\end{lstlisting}
\end{mdframed}
